Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-02-04 revisionMemo/rev1.tex
sync up notes from meeting

@@

	\item Something like if we have dependencies then $E(\hat{B1}) = E(B1) + cov(B1,$ other stuff)}}

@@

@@

		\item Here we have clarified that our study does not address causal identification but instead focuses on providing unbiased estimates of covariates, calibrated confidence intervals that reduce inferential error, and improved predictive performance.  Though we understand these goals are not always central to every political scientists aim, we do believe they relate closely to the field of IR (as demonstrated by the studies we replicate) and a growing interest in forecasting and machine learning in Political Science. (CITE?)

>>>>

		Aronow et al. also explicitly note that their approach does not deal with issues of third order dependence.
		Aronow et al. approach does not deal with bias in parameter estimates.

@@

	\item Something like if we have dependencies then $E(\hat{B1}) = E(B1) + cov(B1,$ other stuff)
	\item SM: needs to add more here to indicate how the existing simulation section is meant to deal with this issue ... onus is on SM to bring in the problems that we highlight in the simulation section to section 2, so readers are clearer on the problem that we are trying to address

@@

		paper by Bai: https://sci-hub.tw/https://onlinelibrary.wiley.com/doi/10.3982/ECTA6135
		connection between LFM and interactive fixed effects?

@@

		\item Here we have clarified that our study does not address causal identification but instead focuses on providing unbiased estimates of covariates, calibrated confidence intervals that reduce inferential error, and improved predictive performance.  Though we understand these goals are not always central to every political scientists aim, we do believe they relate closely to the field of IR (as demonstrated by the studies we replicate) and a growing interest in forecasting and machine learning in Political Science. (CITE?) [add reference to DGM JOP in which AME beat random forest]

### 2020-02-04 revisionMemo/rev2.tex
sync up notes from meeting

@@

@@

@@

		TO DO/CD: We selected our cases based on a few criteria. We focus on studies that are explicitly about International Relations, were published in the last 10 years, and were published in a top ranking general political science outlet (for consistency in editorial standards and reviews, we also decided to focus on one journal, the APSR). We hope that these three criteria ensure that our paper is readable and interpretable to an applied audience. In addition, we selected studies that could help illustrate different key components of the AME approach such as random effects (Reiter and Stam), third-order dependencies (Weeks), precision of fixed effects estimates (Gibler).  While we agree with the reviewer that further replications would effectively demonstrate the benefits of the AME, they are beyond the scope of this paper at this time. (CD to SM: Should we also mention something like ``in consultation with the editor, we believe they are beyond the scope....") 

>>>>

		Reference papers that have thought about what happens when we get the wrong W
		general gist .. spatial models of dyadic dvs are great if we know how to characterize the diffusion amtrices, but the point of our approach is that we may not know how to actually characterize the ways in which actors are related to one another on some diffusion space.
		citations ... flo ... and others based on something that we had researched in the past
		reference franzesse et al mstar framework as a way to operationalize multiple pathways of diffusion in a spatial econometric approach

@@

		in the appendix add more technical description of the estimation process
		SM: figuring out a simulation case where ame fails to show i guess the limitations of it as an estimator ...
		get stats from simulation

@@

		maoz has stuff on linking theories with dependencies
		brandon kinne's paper saom at apsr in which he models the formation of international treaties
		siegel, larson

@@

		TO DO/CD: We selected our cases based on a few criteria. We focus on studies that are explicitly about International Relations, were published in the last 10 years, and were published in a top ranking general political science outlet (for consistency in editorial standards and reviews, we also decided to focus on one journal, the APSR). We hope that these three criteria ensure that our paper is readable and interpretable to an applied audience. In addition, we selected studies that could help illustrate different key components of the AME approach such as random effects (Reiter and Stam), third-order dependencies (Weeks), precision of fixed effects estimates (Gibler).  While we agree with the reviewer that further replications would effectively demonstrate the benefits of the AME, they are beyond the scope of this paper at this time.
